---
title: "Costa Rica Glass"
author: "Julie M. Coulombe"
date: "2/25/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

An analysis of volcanic glass sampled from the Tajo La Florida quarry at Barva Volcano in Costa Rica. Samples collected are from potentially different lava flows. Data was acquired by using an electron microprobe.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
cr_data <- read.csv("data/wt%_probe_data.csv")
library(dbplyr)
library(tidyverse)
library(tinytex)
```


```{r selection, include=FALSE}
rock_cr1a <- cr_data %>%
   filter(grepl("CR1A", cr_data$Comment)) %>%
  mutate("RockName" = "CR1A")
rock_cr1b <- cr_data %>%
  filter(grepl("CR1B", cr_data$Comment)) %>%
  mutate("RockName" = "CR1B")
rock_cr2a <- cr_data %>%
  filter(grepl("CR2A", cr_data$Comment)) %>%
  mutate("RockName" = "CR2A")
rock_cr2b <- cr_data %>%
  filter(grepl("CR2B", cr_data$Comment)) %>%
  mutate("RockName" = "CR2B")
rock_cr3 <- cr_data %>%
  filter(grepl("CR3", cr_data$Comment)) %>%
  mutate("RockName" = "CR3")
rock_cr4 <- cr_data %>%
  filter(grepl("CR4", cr_data$Comment)) %>%
  mutate("RockName" = "CR4")
rock_cr5 <- cr_data %>%
  filter(grepl("CR5", cr_data$Comment)) %>%
  mutate("RockName" = "CR5")
rock_cr7 <- cr_data %>%
  filter(grepl("CR7", cr_data$Comment)) %>%
  mutate("RockName" = "CR7")
rock_data <- rbind(rock_cr1a, rock_cr1b, rock_cr2a, rock_cr2b, rock_cr3, rock_cr4, rock_cr5, rock_cr7)
rock_data <- rock_data[,c(30, 24, 2:16)]
rock_data <- rock_data %>%
  mutate("MgN" = ((MgO / (40.31)) / ((MgO / (40.31)) + (FeO / (71.85)))) * (100))
rock_data$RockName <- as.factor(rock_data$RockName)
```




Data points were constrained as follows:  
 
Wt% Totals > 95.0 and < 101.0  
SiO2 < 90.0  
Al2O3 > 10.0 and < 22.0  
K2O > 1.0  




```{r data constraints, include = FALSE}
rock_data[rock_data == ""] <- NA

rock_data_wt <- rock_data %>%
  select("RockName":"Total", "MgN") %>%  #choose relevant columns
  filter(Total > 95.0 & Total < 101.0) %>% #select rows based on Total
  filter(is.na(V2O3) & SiO2 < 90.0 & Al2O3 < 22.0 & Al2O3 > 10 & K2O > 1.0) #select rows based on elements
```



Create plot for SiO2 vs Na2O + K2O by each rock
```{r silica vs alkali, echo = FALSE, fig.dim = c(10,7)}
alkali_plot <- ggplot(rock_data_wt, aes(x = SiO2, y = Na2O + K2O)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
alkali_plot
```



Create plot for SiO2 vs Mg# by each rock
```{r si vs mg all, echo = FALSE, fig.dim = c(10,7)}
mg_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = MgN)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
mg_plot_all
```
  
    
    


Create plot for SiO2 vs FeO by each rock
```{r si vs fe all, echo = FALSE, fig.dim = c(10,7)}
fe_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = FeO)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
fe_plot_all
```



Create plot for Al2O3 vs TiO by each rock
```{r al vs ti all, echo = FALSE, fig.dim = c(10,7)}
alti_plot_all <- ggplot(rock_data_wt, aes(x = Al2O3, y = TiO2)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
alti_plot_all
```
  
    
    


Create a TAS Diagram as a background layer
```{r tas template, echo = FALSE, fig.dim = c(10,5)}
d = data.frame(x = c(40, 80), y = c(0,15))
theme_set(theme_bw(base_size=28))
#makes the TAS template
p <- ggplot(data=d, mapping=aes(x=x, y=y)) +
  geom_blank() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(limits=c(0,15), expand = c(0, 0)) + 
  scale_x_continuous(limits=c(40,80), expand = c(0, 0)) +
  labs(y=expression(Na[2]*O + K[2]*O*~ wt~'%'), x=expression(SiO[2]*~ wt~'%'))+
  annotate("segment", x=45, xend=45, y=1, yend=5)+
  annotate("segment", x=45, xend=52, y=5, yend=5)+
  annotate("segment", x=52, xend=69, y=5, yend=8)+
  annotate("segment", x=76.5, xend=69, y=1, yend=8)+
  annotate("segment", x=69, xend=69, y=8, yend=13)+
  annotate("segment", x=45, xend=61.32, y=5, yend=13.7)+
  annotate("segment", x=52, xend=52, y=1, yend=5)+
  annotate("segment", x=57, xend=57, y=1, yend=5.9)+
  annotate("segment", x=63, xend=63, y=1, yend=6.9)+
  annotate("segment", x=52, xend=49.4, y=5, yend=7.3)+
  annotate("segment", x=57, xend=53.05, y=5.9, yend=9.25)+
  annotate("segment", x=63, xend=57.6, y=6.9, yend=11.7)+
  annotate("segment", x=41, xend=45, y=3, yend=3)+
  annotate("segment", x=41, xend=41, y=1, yend=3)+
  annotate("segment", x=41, xend=41, y=3, yend=7, linetype="dashed")+
  annotate("segment", x=41, xend=45, y=7, yend=9.4, linetype="dashed")+
  annotate("segment", x=45, xend=52.5, y=9.4, yend=14)+
  annotate("segment", x=49.4, xend=45, y=7.3, yend=9.4)+
  annotate("segment", x=53, xend=48.4, y=9.3, yend=11.5)+
  annotate("segment", x=57.6, xend=50.3, y=11.7, yend=15)
```


```{r template with labels, echo = FALSE, fig.dim = c(10,5)}
tas <- p + annotate("text", label = "Basalt", x = 48.5, y = 2, size=4)+
  annotate("text", label = "Basaltic\n andesite", x = 54.3, y = 3.0, size=4)+
  annotate("text", label = "Andesite", x = 60, y = 3.5, size=4)+
  annotate("text", label = "Dacite", x = 67.5, y = 4.2, size=4)+
  annotate("text", label = "Rhyolite", x = 75, y = 7, size=4)+
  annotate("text", label = "Trachy- \n basalt", x = 48.8, y = 5.7, size=4)+
  annotate("text", label = "Basaltic \n trachy- \n andesite", x = 53, y = 7, size=4)+
  annotate("text", label = "Trachy- \n andesite", x = 57.8, y = 8.2, size=4)+
  annotate("text", label = "Trachydacite", x = 65, y = 9, size=4)+
  annotate("text", label = "Trachyte", x = 62.5, y = 11.5, size=4)+
  annotate("text", label = "Picro- \n basalt", x = 43, y = 1.5, size=4)+
  annotate("text", label = "Basanite \n (Ol > 10%)", x = 43.7, y = 6, size=4)+
  annotate("text", label = "Tephrite \n (Ol < 10%)", x = 45, y = 7.8, size=4)+
  annotate("text", label = "Phono- \n tephrite", x = 48.5, y = 9.5, size=4)+
  annotate("text", label = "Tephri- \n phonolite", x = 52.5, y = 11.5, size=4)+
  annotate("text", label = "Phonolite", x = 57, y = 14, size=4)+
  annotate("text", label = "Foidite", x = 45, y = 12, size=4)
```

```{r print TAS, echo= FALSE, fig.dim = c(8,5)}
tas
```



Plot Alkali by Rock Name
```{r alkali by rockname, echo = FALSE, fig.dim = c(10,7)}
final_alkplot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(x = SiO2, y = Na2O + K2O, colour = RockName, legend(cex = 0.75))) +
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
final_alkplot
```



Overlay Alkali Plot on TAS Diagram
```{r overlay, echo = FALSE, fig.dim = c(10,7)}
tas +
  geom_point(data = rock_data_wt, aes(x = SiO2, y = Na2O + K2O, shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
```



Now to look at plots of all rocks together

Plot Silica vs Mg# by rock
```{r si vs mg, echo = FALSE, fig.dim = c(10,7)}
mg_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, MgN, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3"))
mg_plot <- mg_plot + 
    guides(color = guide_legend(override.aes = list(size = 5))) + 
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
mg_plot + scale_x_continuous(name = "SiO2", limits = c(50, 80))
```



Plot Silica vs Iron by rock
```{r si vs fe, echo = FALSE, fig.dim = c(10,7)}
fe_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, FeO, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3"))
  fe_plot <- fe_plot + 
    guides(color = guide_legend(override.aes = list(size = 5))) +
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
fe_plot + scale_x_continuous(name = "SiO2", limits = c(50, 80))
```



Plot Aluminum vs Titanium by rock
```{r al vs ti, echo = FALSE,  fig.dim = c(10,7)}
alti_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(Al2O3, TiO2, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName)) +
  scale_shape_manual(values = c(7, 8, 21:25, 10)) + 
  scale_color_manual(values = c("coral1", "chartreuse3", "turquoise3", "blue2", "deeppink2", "orchid1", "seagreen3", "firebrick3"))
  alti_plot <- alti_plot + 
    guides(color = guide_legend(override.aes = list(size = 5))) +
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14))
alti_plot
```


