---
title: "Costa Rican Glass Compositions"
author: "Julie M. Coulombe"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  reference_docx: mystyles.docx
  html_document:
    df_print: paged
---

An analysis of volcanic glass sampled from the Tajo La Florida quarry at Barva Volcano in Costa Rica. Samples collected are from potentially different lava flows. Data was acquired by using an electron microprobe.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
cr_data <- read.csv("data/wt%_probe_data.csv")
library(dplyr)
library(tidyverse)
library(huxtable)
options(warn = 2)
```


```{r plot setup, include = FALSE}
plot_symbols <- list(
  scale_shape_manual(values = c(7, 8, 10, 11, 21:25)),
    scale_color_manual(values = c("coral1", "chartreuse3", "peachpuff4",
                                  "blue2", "deeppink2", "orchid3",
                                  "royalblue4", "firebrick3", "cyan3"))
)
plot_theme <- list(
  guides(color = guide_legend(override.aes = list(size = 5))), 
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
)
```


```{r selection, include=FALSE}
rock_cr1a <- cr_data %>%
   filter(grepl("CR1A", cr_data$Comment)) %>%
  mutate("RockName" = "CR1A")
rock_cr1b <- cr_data %>%
  filter(grepl("CR1B", cr_data$Comment)) %>%
  mutate("RockName" = "CR1B")
rock_cr2a <- cr_data %>%
  filter(grepl("CR2A", cr_data$Comment)) %>%
  mutate("RockName" = "CR2A")
rock_cr2b <- cr_data %>%
  filter(grepl("CR2B", cr_data$Comment)) %>%
  mutate("RockName" = "CR2B")
rock_cr3 <- cr_data %>%
  filter(grepl("CR3", cr_data$Comment)) %>%
  mutate("RockName" = "CR3")
rock_cr4 <- cr_data %>%
  filter(grepl("CR4", cr_data$Comment)) %>%
  mutate("RockName" = "CR4")
rock_cr5 <- cr_data %>%
  filter(grepl("CR5", cr_data$Comment)) %>%
  mutate("RockName" = "CR5")
rock_cr6 <- cr_data %>%
  filter(grepl("CR6", cr_data$Comment)) %>%
  mutate("RockName" = "CR6")
rock_cr7 <- cr_data %>%
  filter(grepl("CR7", cr_data$Comment)) %>%
  mutate("RockName" = "CR7")
rock_data <- rbind(rock_cr1a, rock_cr1b, rock_cr2a, rock_cr2b, rock_cr3, rock_cr4, rock_cr5, rock_cr6, rock_cr7)
rock_data <- rock_data[,c(30, 24, 2:16)]
rock_data <- rock_data %>%
  mutate("MgN" = ((MgO / (40.31)) / ((MgO / (40.31)) + (FeO / (71.85)))) * (100))
rock_data$RockName <- as.factor(rock_data$RockName)
```


Data points were constrained as follows:  
 
Wt% Totals > 95.0 and < 101.0  
SiO2 < 90.0  and > 40.0
Al2O3 > 9.0 and < 22.0  
K2O > 1.0  



```{r data constraints, include = FALSE}
rock_data_wt <- rock_data %>%
  select("RockName":"Total", "MgN") %>% 
  filter(Total > 95.0 & Total < 101.0) %>% 
  filter(is.na(V2O3) & SiO2 < 90.0 & SiO2 > 40 & Al2O3 < 22.0 & Al2O3 > 10.0 & K2O > 1.0) 
```



```{r silica vs alkali, echo = FALSE, fig.dim = c(10,7)}
alkali_plot <- ggplot(rock_data_wt, aes(x = SiO2, y = Na2O + K2O)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Silice vs Alkali", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
alkali_plot
```


   
    
    
```{r si vs mg all, echo = FALSE, fig.dim = c(10,7)}
mg_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = MgN)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Silica vs Magnesium Number", x = "SiO2, Wt%", y = "Mg #") + 
  plot_symbols +
  plot_theme
mg_plot_all
```
  
    
  
    
    
```{r si vs fe all, echo = FALSE, fig.dim = c(10,7)}
fe_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = FeO)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Silica vs Iron", x = "SiO2, Wt%", y = "FeO*, Wt%") +
  plot_symbols +
  plot_theme
fe_plot_all
```


```{r si vs ca all, echo = FALSE, fig.dim = c(10,7)}
ca_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = CaO)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Silica vs Calcium", x = "SiO2, Wt%", y = "CaO, Wt%") + 
  plot_symbols +
  plot_theme
ca_plot_all
``` 
  
  
```{r si vs al all, echo = FALSE, fig.dim = c(10,7)}
al_plot_all <- ggplot(rock_data_wt, aes(x = SiO2, y = Al2O3)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Silica vs Aluminum", x = "SiO2, Wt%", y = "Al2O3, Wt%") + 
  plot_symbols +
  plot_theme
al_plot_all
```    
    
```{r al vs ti all, echo = FALSE, fig.dim = c(10,7)}
alti_plot_all <- ggplot(rock_data_wt, aes(x = Al2O3, y = TiO2)) +
  facet_wrap(vars(RockName)) + 
  geom_point(aes(shape = RockName, color = RockName)) +
  labs(title = "Aluminum vs Titanium", x = "Al2O3 Wt%", y = "TiO2 Wt%") +
  plot_symbols +
  plot_theme
alti_plot_all
```
  
 
 
 
 
```{r tas template, include = FALSE, fig.dim = c(10,5)}
d = data.frame(x = c(40, 80), y = c(0,15))
theme_set(theme_bw(base_size=28))
#makes the TAS template
p <- ggplot(data=d, mapping=aes(x=x, y=y)) +
  geom_blank() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(limits=c(0,16), expand = c(0, 0)) + 
  scale_x_continuous(limits=c(40,80), expand = c(0, 0)) +
  labs(y=expression(Na[2]*O + K[2]*O*~ wt~'%'), x=expression(SiO[2]*~ wt~'%'))+
  annotate("segment", x=45, xend=45, y=1, yend=5)+
  annotate("segment", x=45, xend=52, y=5, yend=5)+
  annotate("segment", x=52, xend=69, y=5, yend=8)+
  annotate("segment", x=76.5, xend=69, y=1, yend=8)+
  annotate("segment", x=69, xend=69, y=8, yend=13)+
  annotate("segment", x=45, xend=61.32, y=5, yend=13.7)+
  annotate("segment", x=52, xend=52, y=1, yend=5)+
  annotate("segment", x=57, xend=57, y=1, yend=5.9)+
  annotate("segment", x=63, xend=63, y=1, yend=6.9)+
  annotate("segment", x=52, xend=49.4, y=5, yend=7.3)+
  annotate("segment", x=57, xend=53.05, y=5.9, yend=9.25)+
  annotate("segment", x=63, xend=57.6, y=6.9, yend=11.7)+
  annotate("segment", x=41, xend=45, y=3, yend=3)+
  annotate("segment", x=41, xend=41, y=1, yend=3)+
  annotate("segment", x=41, xend=41, y=3, yend=7, linetype="dashed")+
  annotate("segment", x=41, xend=45, y=7, yend=9.4, linetype="dashed")+
  annotate("segment", x=45, xend=52.5, y=9.4, yend=14)+
  annotate("segment", x=49.4, xend=45, y=7.3, yend=9.4)+
  annotate("segment", x=53, xend=48.4, y=9.3, yend=11.5)+
  annotate("segment", x=57.6, xend=50.3, y=11.7, yend=15)
```


```{r template with labels, echo = FALSE, fig.dim = c(10,5)}
tas <- p + annotate("text", label = "Basalt", x = 48.5, y = 2, size=4)+
  annotate("text", label = "Basaltic\n andesite", x = 54.3, y = 3.0, size=4)+
  annotate("text", label = "Andesite", x = 60, y = 3.5, size=4)+
  annotate("text", label = "Dacite", x = 67.5, y = 4.2, size=4)+
  annotate("text", label = "Rhyolite", x = 75, y = 7, size=4)+
  annotate("text", label = "Trachy- \n basalt", x = 48.8, y = 5.7, size=4)+
  annotate("text", label = "Basaltic \n trachy- \n andesite", x = 53, y = 7, size=4)+
  annotate("text", label = "Trachy- \n andesite", x = 57.8, y = 8.2, size=4)+
  annotate("text", label = "Trachydacite", x = 65, y = 9, size=4)+
  annotate("text", label = "Trachyte", x = 62.5, y = 11.5, size=4)+
  annotate("text", label = "Picro- \n basalt", x = 43, y = 1.5, size=4)+
  annotate("text", label = "Basanite \n (Ol > 10%)", x = 43.7, y = 6, size=4)+
  annotate("text", label = "Tephrite \n (Ol < 10%)", x = 45, y = 7.8, size=4)+
  annotate("text", label = "Phono- \n tephrite", x = 48.5, y = 9.5, size=4)+
  annotate("text", label = "Tephri- \n phonolite", x = 52.5, y = 11.5, size=4)+
  annotate("text", label = "Phonolite", x = 57, y = 14, size=4)+
  annotate("text", label = "Foidite", x = 45, y = 12, size=4)
```

\newpage

Plot Alkali by Rock Name    
    
    
```{r alkali by rockname, echo = FALSE, fig.dim = c(10,7)}
final_alkplot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(x = SiO2, y = Na2O + K2O, colour = RockName, legend(cex = 0.75))) +
  geom_point(aes(shape = RockName, color = RockName, size = 2)) +
  labs(title = "Alkali by Rock Name", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
final_alkplot
```



```{r overlay, echo = FALSE, fig.dim = c(10,7)}
tas +
  geom_point(data = rock_data_wt, aes(x = SiO2, y = Na2O + K2O, shape = RockName, color = RockName)) +
  labs(title = "Rocks Plotted on TAS Diagram", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
```

\newpage

Now to look at plots of all rocks together

   
    
    
```{r si vs mg, echo = FALSE, fig.dim = c(10,7)}
mg_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, MgN, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Silica vs Magnesium", x = "SiO2, Wt%", y = "Mg #") +
  plot_symbols +
  plot_theme
mg_plot + scale_x_continuous(limits = c(50, 80))
```



```{r si vs fe, echo = FALSE, fig.dim = c(10,7)}
fe_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, FeO, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Silica vs Iron", x = "SiO2, Wt%", y = "FeO*, Wt%") +
  plot_symbols +
  plot_theme
fe_plot + scale_x_continuous(limits = c(50, 80))
```


```{r si vs ca, echo = FALSE, fig.dim = c(10,7)}
ca_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, CaO, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Silica vs Calcium", x = "SiO2, Wt%", y = "CaO, Wt%") +
  plot_symbols +
  plot_theme
ca_plot + scale_x_continuous(limits = c(50, 80))
```


```{r si vs ti, echo = FALSE, fig.dim = c(10,7)}
ti_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, TiO2, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Silica vs Aluminum", x = "SiO2, Wt%", y = "TiO2, Wt%") +
  plot_symbols +
  plot_theme
ti_plot + scale_x_continuous(limits = c(50, 80))
```


```{r si vs al, echo = FALSE, fig.dim = c(10,7)}
al_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, Al2O3, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Silica vs Aluminum", x = "SiO2, Wt%", y = "Al2O3, Wt%") +
  plot_symbols +
  plot_theme
al_plot + scale_x_continuous(limits = c(50, 80))
```   
    
    
```{r al vs ti, echo = FALSE,  fig.dim = c(10,7)}
alti_plot <- rock_data_wt %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(Al2O3, TiO2, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Aluminum vs Titanium", x = "Al2O3, Wt%", y = "TiO2, Wt%") +
  plot_symbols +
  plot_theme
alti_plot
```


\newpage

```{r glass avg df, include=FALSE}
gls_avg <- rock_data_wt %>%
  group_by(RockName) %>%
  summarise("SiO2" = mean(SiO2), "TiO2" = mean(TiO2),
            "Al2O3" = mean(Al2O3), "Cr" = mean(Cr2O3),
            "MgO" = mean(MgO), "CaO" = mean(CaO), "MnO" = mean(MnO),
            "FeO" = mean(FeO), "Na2O" = mean(Na2O), "K2O" = mean(K2O),
            "S" = mean(S), "P2O5" = mean(P2O5), "MgN" = mean(MgN),
            "Total" = mean(Total))
```

```{r glass avg alk, echo = FALSE, fig.dim = c(10,7)}
avg_alkplot <- gls_avg %>%
  ggplot(mapping = aes(x = SiO2, y = Na2O + K2O, colour = RockName, legend(cex = 0.75))) +
  geom_point(aes(shape = RockName, color = RockName, size = 2)) +
  labs(title = "Average Glass Alkali per Rock", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
avg_alkplot
```

```{r avg alk on TAS, echo = FALSE, fig.dim = c(10,7)}
tas +
  geom_point(data = gls_avg, aes(x = SiO2, y = Na2O + K2O, shape = RockName, color = RockName, size = 3)) +
  labs(title = "Average Glass Plotted on TAS Diagram", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
```

\newpage

```{r mg avg, echo=FALSE, fig.dim = c(10,7)}
mg_avg_plot <- gls_avg %>%
  ggplot(mapping = aes(SiO2, MgN, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName), size = 3) +
  labs(title = "Average Silica vs Magnesium Number by rock", x = "SiO2, Wt%", y = "Mg #") +
  plot_symbols +
  plot_theme
mg_avg_plot + scale_x_continuous(limits = c(55,80))
```

```{r fe avg, echo=FALSE, fig.dim = c(10,7)}
fe_avg_plot <- gls_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, FeO, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Average Silica vs Iron by Rock", x = "SiO2, Wt%", y = "FeO*, Wt%") +
  plot_symbols +
  plot_theme
fe_avg_plot + scale_x_continuous(limits = c(50, 80))
```

```{r ca avg, echo=FALSE, fig.dim = c(10,7)}
ca_avg_plot <- gls_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, CaO, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Average Silica vs Calcium by Rock", x = "SiO2, Wt%", y = "CaO, Wt%") +
  plot_symbols +
  plot_theme
ca_avg_plot + scale_x_continuous(limits = c(50, 80))
```

```{r al avg, echo=FALSE, fig.dim = c(10,7)}
al_avg_plot <- gls_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(SiO2, Al2O3, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Average Silica vs Aluminum by Rock", x = "SiO2, Wt%", y = "Al2O3, Wt%") +
  plot_symbols +
  plot_theme
```

```{r alti avg, echo=FALSE, fig.dim = c(10,7)}
alti_avg_plot <- gls_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(Al2O3, TiO2, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Average Aluminum vs Titanium by Rock", x = "Al2O3, Wt%", y = "TiO2, Wt%") +
  plot_symbols +
  plot_theme
alti_avg_plot
```

\newpage



Table laying out representative glass samples

```{r glass table, echo=FALSE}
cr_data <- cr_data %>%
  select("Comment", "SiO2":"S", "P2O5", "Total")
cr_data2 <- cr_data[,-1]  
rownames(cr_data2) <- cr_data[,1] 
cr_data2 <- as.matrix(cr_data2)  
cr_data2_trans <- t(cr_data2)  
cr_data2_trans2 <- as.data.frame(cr_data2_trans)

cr_table1 <- cr_data2_trans2 %>% 
 select("CR1A2_2 Pt1", "CR1B_1 Pt15", "CR2A2_3 PT1", "CR2B2_1 PT2", "CR31_3 PT7", "CR42_1 PT6", "CR51_2 PT5", "CR72_3 Pt1") %>%
  drop_na()
cr_table1_tb <- rownames_to_column(cr_table1, var = "wt %") %>%
  as_tibble()
cr_table1_tb
```

\newpage


Table showing glass averages

```{r gls avg tbl, echo=FALSE}
glass_avg <- rock_data_wt %>%
  group_by(RockName) %>%
    summarise(n = n(),
            "SiO2 m" = mean(SiO2), "SiO2 sd" = sd(SiO2),
            "TiO2 m" = mean(TiO2), "TiO2 sd" = sd(TiO2),
            "Al2O3 m" = mean(Al2O3), "Al2O3 sd" = sd(Al2O3),
            "Cr m" = mean(Cr2O3), "CR sd" = sd(Cr2O3),
            "MgO m" = mean(MgO), "MgO sd" = sd(MgO), 
            "CaO m" = mean(CaO), "CaO sd" = sd(CaO),
            "MnO m" = mean(MnO), "MnO sd" = sd(MnO),
            "FeO m" = mean(FeO), "FeO sd" = sd(FeO),
            "Na2O m" = mean(Na2O), "Na2O sd" = sd(Na2O),
            "K2O m" = mean(K2O), "K2O sd" = sd(K2O),
            "S m" = mean(S), "S sd" = sd(S),
            "P2O5 m" = mean(P2O5), "P2O5 sd" = sd(P2O5),
            "MgN m" = mean(MgN), "MgN sd" = sd(MgN),
            "Total m" = mean(Total), "Total sd" = sd(Total), .groups = "keep")
glass_avg <- as.data.frame(glass_avg)
glass_avg
```




\newpage

```{r gls avg alk, echo=FALSE, fig.dim = c(10,7)}
alk_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, y = `Na2O m` + `K2O m`,
                       ymin = `Na2O m` + `K2O m` - `Na2O sd` - `K2O sd`,
                       ymax = `Na2O m` + `K2O m` + `Na2O sd` + `K2O sd`,
                       colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Alk by Rock", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  plot_symbols +
  plot_theme
alk_avg_glsplot
```


```{r gls avg mg, echo=FALSE, fig.dim = c(10,7)}
mg_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `MgO m`, ymin = `MgO m` - `MgO sd`, ymax = `MgO m` + `MgO sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Mg by Rock", x = "SiO2, Wt%", y = "MgO, Wt%") +
  plot_symbols +
  plot_theme
mg_avg_glsplot
```

```{r gls avg fe, echo=FALSE, fig.dim = c(10,7)}
fe_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `FeO m`, ymin = `FeO m` - `FeO sd`, ymax = `FeO m` + `FeO sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Iron by Rock", x = "SiO2, Wt%", y = "FeO, Wt%") +
  plot_symbols +
  plot_theme
fe_avg_glsplot
```

```{r gls avg ca, echo=FALSE, fig.dim = c(10,7)}
ca_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `CaO m`, ymin = `CaO m` - `CaO sd`, ymax = `CaO m` + `CaO sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Calcium by Rock", x = "SiO2, Wt%", y = "CaO, Wt%") +
  plot_symbols +
  plot_theme
ca_avg_glsplot
```

```{r gls avg k, echo=FALSE, fig.dim = c(10,7)}
k_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `K2O m`, ymin = `K2O m` - `K2O sd`,
                       ymax = `K2O m` + `K2O sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs K by Rock", x = "SiO2, Wt%", y = "K2O, Wt%") +
  plot_symbols +
  plot_theme
k_avg_glsplot
```

```{r gls avg ti, echo=FALSE, fig.dim = c(10,7)}
ti_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `TiO2 m`, ymin = `TiO2 m` - `TiO2 sd`,
                       ymax = `TiO2 m` + `TiO2 sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Ti by Rock", x = "SiO2, Wt%", y = "TiO2, Wt%") +
  plot_symbols +
  plot_theme
ti_avg_glsplot
```

```{r gls avg al, echo=FALSE, fig.dim = c(10,7)}
al_avg_glsplot <- glass_avg %>%
  group_by(RockName) %>%
  ggplot(mapping = aes(`SiO2 m`, `Al2O3 m`, ymin = `Al2O3 m` - `Al2O3 sd`,
                       ymax = `Al2O3 m` + `Al2O3 sd`, colour = RockName)) +
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  geom_errorbar() +
  labs(title = "Glass Average Silica vs Al2O3 by Rock", x = "SiO2, Wt%", y = "Al2O3, Wt%") +
  plot_symbols +
  plot_theme
al_avg_glsplot
```


\newpage

Taking a look at comparing CR1A to CR1B (two samples from the same flow)

```{r 1a to 1b glass - si/alk, echo=FALSE, fig.dim = c(10,7)}
cr1a_cr1b_alk <- rock_data_wt %>%
  filter(grepl("CR1", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, Na2O + K2O, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR1A to CR1B Silica to Alkali", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  scale_shape_manual(values = c(7, 8)) + 
  scale_color_manual(values = c("coral1", "chartreuse3")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr1a_cr1b_alk + scale_x_continuous(limits = c(50, 80))
```


```{r 1a to 1b glass - si/mg, echo=FALSE, fig.dim = c(10,7)}
cr1a_cr1b_mg <- rock_data_wt %>%
  filter(grepl("CR1", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, MgN, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR1A to CR1B Silica to Mg#", x = "SiO2, Wt%", y = "Mg #") +
  scale_shape_manual(values = c(7, 8)) + 
  scale_color_manual(values = c("coral1", "chartreuse3")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr1a_cr1b_mg + scale_x_continuous(limits = c(50, 80))
```

```{r 1a to 1b glass - si/fe, echo=FALSE, fig.dim = c(10,7)}
cr1a_cr1b_fe <- rock_data_wt %>%
  filter(grepl("CR1", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, FeO, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR1A to CR1B Silica to Iron", x = "SiO2, Wt%", y = "FeO*, Wt%") +
  scale_shape_manual(values = c(7, 8)) + 
  scale_color_manual(values = c("coral1", "chartreuse3")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr1a_cr1b_fe + scale_x_continuous(limits = c(50, 80))
```

```{r 1a to 1b glass - Al/Ti, echo=FALSE, fig.dim = c(10,7)}
cr1a_cr1b_alti <- rock_data_wt %>%
  filter(grepl("CR1", rock_data_wt$RockName)) %>%
  ggplot(aes(Al2O3, TiO2, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparsion of CR1A to CR1B Aluminum to Titanium", x = "Al2O3, Wt%", y = "TiO2, Wt%") +
  scale_shape_manual(values = c(7, 8)) + 
  scale_color_manual(values = c("coral1", "chartreuse3")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr1a_cr1b_alti
```

\newpage

Taking a look at comparing CR2A to CR2B

```{r 2a to 2b glass - si/alk, echo=FALSE, fig.dim = c(10,7)}
cr2a_cr2b_alk <- rock_data_wt %>%
  filter(grepl("CR2", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, Na2O + K2O, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR2A to CR2B Silica to Alkali", x = "SiO2, Wt%", y = "Na2O + K2O, Wt%") +
  scale_shape_manual(values = c(10, 11)) + 
  scale_color_manual(values = c("peachpuff4", "blue2")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
    theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr2a_cr2b_alk + scale_x_continuous(limits = c(50, 80))
```


```{r 2a to 2b glass - si/mg, echo=FALSE, fig.dim = c(10,7)}
cr2a_cr2b_mg <- rock_data_wt %>%
  filter(grepl("CR2", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, MgN, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR2A to CR2B Silica to Mg#", x = "SiO2, Wt%", y = "Mg #") +
  scale_shape_manual(values = c(10, 11)) + 
  scale_color_manual(values = c("peachpuff4", "blue2")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr2a_cr2b_mg + scale_x_continuous(limits = c(50, 80))
```

```{r 2a to 2b glass - si/fe, echo=FALSE, fig.dim = c(10,7)}
cr2a_cr2b_fe <- rock_data_wt %>%
  filter(grepl("CR2", rock_data_wt$RockName)) %>%
  ggplot(aes(SiO2, FeO, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR2A to CR2B Silica to Iron", x = "SiO2, Wt%", y = "FeO*, Wt%") +
  scale_shape_manual(values = c(10, 11)) + 
  scale_color_manual(values = c("peachpuff4", "blue2")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr2a_cr2b_fe + scale_x_continuous(limits = c(50, 80))
```

```{r 2a to 2b glass - Al/Ti, echo=FALSE, fig.dim = c(10,7)}
cr2a_cr2b_alti <- rock_data_wt %>%
  filter(grepl("CR2", rock_data_wt$RockName)) %>%
  ggplot(aes(Al2O3, TiO2, colour = RockName)) + 
  geom_point(aes(shape = RockName, color = RockName, size = 3)) +
  labs(title = "Comparision of CR2A to CR2B Aluminum to Titanium", x = "Al2O3, Wt%", y = "TiO2, Wt%") +
  scale_shape_manual(values = c(10, 11)) + 
  scale_color_manual(values = c("peachpuff4", "blue2")) + 
  guides(color = guide_legend(override.aes = list(size = 5))) +
  theme(text = element_text(size = 15),
          legend.key.size = unit(1.0, "cm"),
          legend.title = element_text(size = 14),
          plot.title = element_text(hjust = 0.5))
cr2a_cr2b_alti
```
